Catchy Title

### 2011-10-11 proposal/paper.tex
Plan of work

>>>>

\section{Plan of Work}
\begin{tabular}{lll}
\bf Member & \bf Project Portion & \bf Papers Read \\
Yoshihisa Abe & & \cite{Zhu2002}, \cite{Zhu2003}, \cite{Sakurai2011} \\
Ilari Shafer & IPCA application/extension, scalability & \cite{Li2009}, \cite{Gmach2007}, \cite{Lavrenko2000} \\
Kai Ren & Data Collection and Preparation, Anomaly Detection Experiment &  \cite{xu2009}, \cite{xu2010}, \cite{nguyen2011} \\
Vishnu Boddeti & Kalman Filter Models & \cite{papadimitriou2005streaming}, \cite{roweis1999unifying}
\end{tabular}
